\subsubsection{Synapses}

Let $v, w \in V$ be the pre- and postsynaptic neurons, respectively, and let $(v \to w) \in E$ be the electrically conductive link (synapse) between them. When a spike arrives at the synapse, it triggers the release of a neurotransmitter: AMPA when $\type(v) = \ex$, and GABA when $\type(v) = \inh$ \cite{Lowet2015}.

A synaptic gate can be thought of as a transistor that influences the synaptic transmission, it can amplify and switch electrical signals. It is located on the postsynaptic neuron $w$ and modifies the conductance of electrical signals by changing its state. The gating value includes the rise $\synapticrise$ and decay $\synapticdecay$ times and the transmission concentration term to mediate the interneural signal transmission \cite{Destexhe1994}.

For a given neuron, it is assumed that the dynamics of all its synapses are synchronized. Therefore, although a synaptic gate is located on the postsynaptic neuron $w$, it follows the potential and gating parameters of the presynaptic neuron $v$ \cite{Lowet2015}. Hence, $s_{(v \to w)} \to \synapticgate_v$, and then the gating value can be obtained from the following differential equation:
\begin{gather}
    \frac{d\synapticgate_v}{dt} = \synapticrise_{\type(v)} \underbrace{\left( 1 + \tanh \left( \frac{p_{v}}{4} \right) \right)}_{T_v: \text{trans. conc.}} (1 - \synapticgate_v) - \frac{\synapticgate_v}{\synapticdecay_{\type(v)}}, \\
    \label{eq:synaptic-gates}
    \synapticgate_v(0) = 0.
\end{gather}
The values for the synaptic parameters are presented in Table \ref{tab:synaptic-current-params}.

\begin{table}[!htp] 
    \centering
    \input{assets/tables/synaptic-current-params}
    \caption[Synaptic parameters]{Synaptic parameter values for AMPA and GABA neurotransmitters \cite{Lowet2015}.}
    \label{tab:synaptic-current-params}
\end{table}


As mentioned in Section \ref{sec:action-potential}, the spike initiating threshold for excitatory neurons is between $-60$ and $-40$ mV. When the neuron is at rest, that is $p_v < -40$ mV, the transmission concentration is at its minimum:
\begin{gather}
\begin{split}
    & T_v = 1 + \tanh \left( \frac{p_{v}}{4} \right) \approx 0 \\
    \Rightarrow \ & \frac{d\synapticgate_v}{dt} \approx - \frac{\synapticgate_v}{\synapticdecay_{\type(v)}}.
\end{split}
\end{gather}
This implies that the gating decays exponentially.
So, in between spikes, the conductance and thus the synaptic input from the neuron $v$ decreases. 

During an action potential, the membrane potential reaches $p_v > 10$. Thus, the transmission concentration is at its maximum, and
\begin{gather}
\begin{split}
    & T_v = 1 + \tanh \left( \frac{p_{v}}{4} \right) \approx 2 \\
    \Rightarrow \ & \frac{d\synapticgate_v}{dt} \approx 2 \cdot \synapticrise_{\type(v)} (1 - \synapticgate_v) - \frac{\synapticgate_v}{\synapticdecay_{\type(v)}},
\end{split}
\end{gather}
which indicates that the gating rises during the action potential and falls once it is over. 